Contextual Combinatorial Cascading Bandits

### 2015-12-10 contextual combinatorial cascading bandits.tex

\begin{theorem}[\cite{abbasi2011improved}]
\label{thm:theta_estimate}
Let 
%$$
%\beta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\det(\lambda I)}\right) + 2 \ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}.
%$$
%\wei{I thought the following is simpler. Should we use the following?}
$$
\bbeta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\lambda^d \delta^2}\right)} + \sqrt{\lambda}.
$$
Then for any $\delta > 0$, with probability at least $1 - \delta$, for all $t > 0$, we have
\begin{equation}
\label{eq:estimateTheta}
\norm{\hat{\theta}_t - \theta_{\ast}}_{\bV_{t}} \leq \bbeta_{t}(\delta).
\end{equation}
\end{theorem}

@@

\begin{lemma} % det(V_t)
\label{lem:detVt}
$\det(\bV_t)$ is increasing with respect to $t$ and 
$$
\det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.
$$
\end{lemma}
\begin{proof}
To prove $\det(\bV_t)$ is increasing with respect to $t$, it is enough to prove that
$$
\det(V + xx^{\top}) \geq \det(V)
$$
for any symmetric positive definite matrix $V \in \RR^{d \times d}$ and column vector $x \in \RR^{d\times 1}$. In fact,
\begin{align*}
&\det(V + xx^{\top}) \\
=& \det(V) \det(I + V^{-1/2}x x^{\top} V^{-1/2})\\
=& \det(V) \det(1 + \norm{V^{-1/2}x}^2)\\
\geq &\det(V).
\end{align*}
The second equality is because Sylvester's determinant theorem, which states that $\det(I + AB) = \det(I +BA)$.

Let the eigenvalues of $\bV_t$ be $\lambda_1, \ldots, \lambda_d > 0$. Then
\begin{align*}
&\det(\bV_t) = \lambda_1 \cdot \cdots \cdot \lambda_d \\
\leq & \left( \frac{\lambda_1 + \ldots + \lambda_d}{d} \right)^d = (\trace(\bV_t)/d)^d.
\end{align*}
\wei{Why? need a citation?} \shuai{I have rewritten this part.}
Also,
\begin{align*}
&\trace(\bV_t)\\
& = \trace(\lambda I) + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \trace(x_{s,\ba_k^s} x_{s,\ba_k^s}^{\top})\\	
& = d \lambda + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \norm{x_{s,\ba_k^s}}_2^2\\
& \leq d \lambda + \sum_{s=1}^t\sum_{k=1}^{K}\gamma_k^2 = d \lambda + t C_\gamma.
\end{align*}
Thus we have $\det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.$
\end{proof}

\begin{lemma}
\label{lem:SumXiEstimateInDet}
Let $x_i \in \RR^{d \times 1}, 1 \leq i \leq n$. Then we have
$$
\det\left(I + \sum_{i=1}^n x_i x_i^{\top}\right) \geq 1 + \sum_{i=1}^n \norm{x_i}_2^2.
$$
\end{lemma}
\begin{proof}
Denote the eigenvalues of $I + \sum_{i=1}^n x_i x_i^{\top}$ by $1+\alpha_1,...,1+\alpha_d$ with $\alpha_j \geq 0$, $1\leq j\leq d$. Then
\begin{align*}
&\det(I + \sum_{i=1}^n x_i x_i^{\top})= \prod_{j=1}^d (1 + \alpha_j)\\
&\geq 1 +\sum_{j=1}^d \alpha_j =1-d + \sum_{i=1}^d (1+\alpha_i) \\
&=1-d + \trace(I + \sum_{i=1}^n x_i x_i^{\top})= 1-d + d + \sum_{i=1}^n \norm{x_i}_2^2\\
&=1 + \sum_{i=1}^n \norm{x_i}_2^2.
\end{align*}
\end{proof}

\begin{lemma}
If $\lambda \geq C_\gamma$, then
$$
\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln \left(\frac{\det(\bV_t)}{\lambda^d} \right).
$$
\end{lemma}
\begin{proof}
\begin{align*}
&\det(\bV_t) = \det(\bV_{t-1} + \sum_{k=1}^{\bO_t} (\gamma_k X_{t,\ba_k^{t}})(\gamma_k X_{t, \ba_k^{t}}^{\top}))\\
&=\det(\bV_{t-1})\\
&~~~\cdot \det(I + \sum_{k=1}^{\bO_t} \gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}} (\gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}})^{\top})\\
&\geq \det(\bV_{t-1}) (1 + \sum_{k=1}^{\bO_t} \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2)\\
&\geq \det(\lambda I)\prod_{s=1}^{t}(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)
\end{align*}
Because
$$
\norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \norm{\gamma_k x_{s,\ba_k^s}}_2^2/\lambda_{\min}(\bV_{s-1}) \leq \gamma_k^2 /\lambda,
$$
we have 
$$
\sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \frac{1}{\lambda} \sum_{k=1}^{K} \gamma_k^2 = C_\gamma /\lambda \leq 1
$$
Using the fact that $ 2\ln(1+u) \geq u$ for any $u \in [0,1]$, we get
\begin{align*}
&\sum_{s=1}^t \sum_{k=1}^{\bO_s}\norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \\
&\leq 2\sum_{s=1}^t\ln(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)\\
&\leq 2(\ln(\det(\bV_t)) - \ln(\det(\lambda I))) \\
&= 2 \ln \left(\frac{\det(\bV_t)}{\det(\lambda I)} \right)
\end{align*}
\end{proof}

\begin{proof}[ of Theorem \ref{thm:main}]
Suppose inequality (\ref{eq:estimateTheta}) holds for all time $t$.

For the disjunctive case,
\begin{equation}
\begin{split}
&R(T) = \EE[\sum_{t=1}^{T} \EE_{t}[R(t, \bA_t)] ]\\
&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t \left[\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right]\\
&\leq \EE \left[\frac{1}{p^*} \bbeta_T(\delta) \sqrt{\left(\sum_{t=1}^{T} \bO_t\right) \left( \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)}
	\right ]  \\
&\leq \EE\left[\frac{1}{p^*} \left( \sqrt{ \ln \left( \frac{\det(\bV_T)}{\lambda^d \delta^2} \right)} + \sqrt{\lambda} \right) \right. \\
& \left. \qquad \qquad \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right]\\
&\leq \frac{\sqrt{2}}{p^*} \left(\sqrt{ d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2} \right) } + \sqrt{\lambda} \right)\\
&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} ]
\end{split}
\end{equation}
The first inequality is by Lemma \ref{lem:DeltaEsimateWithP*}. The second inequality is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by definition of $\bbeta_t(\delta)$ and Lemma \ref{lem:detVt}, and mean inequality. The third inequality is because of the definition of $\beta_t(\delta)$ and Lemma \ref{lem:SumXiEstimateInDet}. And the last inequality is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.

Similarly, for the conjunctive case, 
\begin{equation}
\begin{split}
&R(T) = \EE[ \sum_{t=1}^{T} \EE_{t}[R_{\wedge}(t, \bA_t)] ]\\
&\leq \EE \left[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \EE_t\left[\bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \right] \\
&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \bbeta_{T}(\delta) \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \bbeta_{T}(\delta) \sqrt{ \left(\sum_{t=1}^{T} \bO_t \right) \EE_t \left[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]} \right]\\
&\leq \EE \left[\frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{\ln\left(\frac{\det(\bV_T)}{\lambda^d \delta^2}\right) } + \sqrt{\lambda} \right) \right. \\
&\qquad \qquad \left. \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right]\\
&\leq \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2}\right) } + \sqrt{\lambda} \right)\\
&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} ]
\end{split}
\end{equation}
\end{proof}

The first inequality is by Lemma \ref{lem:DeltaEsimateWithP*}. The second inequality is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by definition of $\bbeta_t(\delta)$ and Lemma \ref{lem:detVt}. The third inequality is because of mean inequality. The forth inequality is by the definition of $\beta_t(\delta)$ and Lemma \ref{lem:SumXiEstimateInDet}. And the last inequality is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.

>>>>

\begin{theorem}[\cite{abbasi2011improved}]
\label{thm:theta_estimate}
Let 
%$$
%\beta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\det(\lambda I)}\right) + 2 \ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}.
%$$
%\wei{I thought the following is simpler. Should we use the following?}
\begin{equation}
\bbeta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\lambda^d \delta^2}\right)} + \sqrt{\lambda}. \label{eq:definebeta}
\end{equation}
Then for any $\delta > 0$, with probability at least $1 - \delta$, for all $t > 0$, we have
\begin{equation}
\label{eq:estimateTheta}
\norm{\hat{\theta}_t - \theta_{\ast}}_{\bV_{t}} \leq \bbeta_{t}(\delta).
\end{equation}
\end{theorem}

@@

From the above lemma, we can bound the regret at time $t$ in terms of the observed base arms, for which we further bound in Lemma~\ref{lem:SumXiEstimateInDet}.
But before that, we need the following technical lemma.

\begin{lemma}
\label{lem:detTech}
Let $x_i \in \RR^{d \times 1}, 1 \leq i \leq n$. Then we have
$$
\det\left(I + \sum_{i=1}^n x_i x_i^{\top}\right) \geq 1 + \sum_{i=1}^n \norm{x_i}_2^2.
$$
\end{lemma}
\begin{proof}
Denote the eigenvalues of $I + \sum_{i=1}^n x_i x_i^{\top}$ by $1+\alpha_1,...,1+\alpha_d$ with $\alpha_j \geq 0$, $1\leq j\leq d$. Then
\begin{align*}
&\det(I + \sum_{i=1}^n x_i x_i^{\top})= \prod_{j=1}^d (1 + \alpha_j)\\
&\geq 1 +\sum_{j=1}^d \alpha_j =1-d + \sum_{i=1}^d (1+\alpha_i) \\
&=1-d + \trace(I + \sum_{i=1}^n x_i x_i^{\top})= 1-d + d + \sum_{i=1}^n \norm{x_i}_2^2\\
&=1 + \sum_{i=1}^n \norm{x_i}_2^2.
\end{align*}
\end{proof}

\begin{lemma}
\label{lem:SumXiEstimateInDet}
If $\lambda \geq C_\gamma$, then
$$
\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln \left(\frac{\det(\bV_t)}{\lambda^d} \right).
$$
\end{lemma}
\begin{proof}
\begin{align}
&\det(\bV_t) = \det\left(\bV_{t-1} + \sum_{k=1}^{\bO_t} (\gamma_k x_{t,\ba_k^{t}})(\gamma_k x_{t, \ba_k^{t}}^{\top}) \right) \nonumber \\
&=\det(\bV_{t-1}) \notag \\
&~~~\cdot \det \left(I + \sum_{k=1}^{\bO_t} \gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}} (\gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}})^{\top} \right) \label{eq:Vfactor}\\
&\geq \det(\bV_{t-1}) \left(1 + \sum_{k=1}^{\bO_t} \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right) \label{eq:detGeq} \\
&\geq \det(\lambda I)\prod_{s=1}^{t} \left(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \right), \label{eq:repeatV}
\end{align}
where Equality~\eqref{eq:Vfactor} is by the fact that
	$V+U = V^{1/2} (I + V^{-1/2} U V^{-1/2}) V^{1/2}$ for a symmetric positive definite
	matrix $V$, Inequality \eqref{eq:detGeq} is due to Lemma \ref{lem:detTech}, and
	Inequality~\eqref{eq:repeatV} is by repeatedly applying Inequality
	\eqref{eq:detGeq}.

Because
$$
\norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \norm{\gamma_k x_{s,\ba_k^s}}_2^2/\lambda_{\min}(\bV_{s-1}) \leq \gamma_k^2 /\lambda,
$$
where $\lambda_{\min}(\bV_{s-1})$ is the minimum eigenvalue of
	$\bV_{s-1}$,  we have 
$$
\sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \frac{1}{\lambda} \sum_{k=1}^{K} \gamma_k^2 = C_\gamma /\lambda \leq 1
$$
Using the fact that $ 2\ln(1+u) \geq u$ for any $u \in [0,1]$, we get
\begin{align*}
&\sum_{s=1}^t \sum_{k=1}^{\bO_s}\norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \\
&\leq 2\sum_{s=1}^t\ln \left(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \right)\\
& = 2 \ln \prod_{s=1}^{t} \left(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \right) \\
&\le 2 \ln \left(\frac{\det(\bV_t)}{\det(\lambda I)} \right),
\end{align*}
where the last inequality is from Inequality~\eqref{eq:repeatV}.
\end{proof}

Finally the last lemma bound $\det(\bV_t)$.

\begin{lemma} % det(V_t)
\label{lem:detVt}
$\det(\bV_t)$ is increasing with respect to $t$ and 
$$
\det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.
$$
\end{lemma}
\begin{proof}
To prove $\det(\bV_t)$ is increasing with respect to $t$, it is enough to prove that
$$
\det(V + xx^{\top}) \geq \det(V),
$$
for any symmetric positive definite matrix $V \in \RR^{d \times d}$ and column vector $x \in \RR^{d\times 1}$. In fact,
\begin{align*}
&\det(V + xx^{\top}) \\
=& \det(V) \det(I + V^{-1/2}x x^{\top} V^{-1/2})\\
=& \det(V) \det(1 + \norm{V^{-1/2}x}^2)\\
\geq &\det(V).
\end{align*}
The second equality above is due to Sylvester's determinant theorem, which states that $\det(I + AB) = \det(I +BA)$.

Let the eigenvalues of $\bV_t$ be $\lambda_1, \ldots, \lambda_d > 0$. Then
\begin{align*}
&\det(\bV_t) = \lambda_1 \cdot \cdots \cdot \lambda_d \\
\leq & \left( \frac{\lambda_1 + \ldots + \lambda_d}{d} \right)^d = (\trace(\bV_t)/d)^d.
\end{align*}
Also,
\begin{align*}
&\trace(\bV_t)\\
& = \trace(\lambda I) + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \trace(x_{s,\ba_k^s} x_{s,\ba_k^s}^{\top})\\	
& = d \lambda + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \norm{x_{s,\ba_k^s}}_2^2\\
& \leq d \lambda + \sum_{s=1}^t\sum_{k=1}^{K}\gamma_k^2 = d \lambda + t C_\gamma.
\end{align*}
Thus we have $\det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.$
\end{proof}

Now we are ready to prove the main theorem.

\begin{proof}[ of Theorem \ref{thm:main}]
Suppose inequality (\ref{eq:estimateTheta}) holds for all time $t$, which is
	true with probability $1-\delta$.

For the disjunctive case, we have
\begin{align}
&R(T) = \EE \left[\sum_{t=1}^{T} \EE_{t}[R(t, \bA_t)] \right] \notag\\
&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t \left[\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMdeltaEst}\\
&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \bbeta_{T}(\delta) \EE_t \left[ \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMbeta}\\
&\leq \EE \left[\frac{1}{p^*} \bbeta_T(\delta) \sqrt{\left(\sum_{t=1}^{T} \bO_t\right) \left( \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)}
	\right ]  \label{eq:pfMmeanEq}\\
&\leq \EE\left[\frac{1}{p^*} \left( \sqrt{ \ln \left( \frac{\det(\bV_T)}{\lambda^d \delta^2} \right)} + \sqrt{\lambda} \right) \right. \notag\\
& \left. \qquad \qquad \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right] \label{eq:pfMsumXi}\\
&\leq \frac{\sqrt{2}}{p^*} \left(\sqrt{ d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2} \right) } + \sqrt{\lambda} \right) \notag\\
&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}. \label{eq:pfMdetEst}
\end{align}
Inequality \eqref{eq:pfMdeltaEst} is by Lemma \ref{lem:DeltaEsimateWithP*}. 
Inequality \eqref{eq:pfMbeta} is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by the definition of $\bbeta_t(\delta)$ 
	(Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:detVt}. 
Inequality \eqref{eq:pfMmeanEq} is by the mean inequality. 
Inequality \eqref{eq:pfMsumXi} is because of the definition of $\beta_t(\delta)$ (Eq.\eqref{eq:definebeta}) 
	and Lemma \ref{lem:SumXiEstimateInDet}. 
And the last inequality \eqref{eq:pfMdetEst} is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.

Similarly, for the conjunctive case, we have the following derivation:
\begin{align}
&R(T) = \EE \left[ \sum_{t=1}^{T} \EE_{t}[R_{\wedge}(t, \bA_t)] \right] \notag\\
&\leq \EE \left[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \EE_t\left[\bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \right] \label{eq:pfMCdeltaEst}\\
&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \bbeta_{T}(\delta) \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \label{eq:pfMCbeta}\\
&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \bbeta_{T}(\delta) \sqrt{ \left(\sum_{t=1}^{T} \bO_t \right) \EE_t \left[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]} \right] \label{eq:pfMCmeaneq}\\
&\leq \EE \left[\frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{\ln\left(\frac{\det(\bV_T)}{\lambda^d \delta^2}\right) } + \sqrt{\lambda} \right) \right. \notag\\
&\qquad \qquad \left. \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right] \label{eq:pfMCsumXi}\\
&\leq \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2}\right) } + \sqrt{\lambda} \right) \notag\\
&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}. \label{eq:pfMCdetEst}
\end{align}
%The first inequality \eqref{eq:pfMCdeltaEst} is by Lemma \ref{lem:DeltaEsimateWithP*}. The second inequality \eqref{eq:pfMCbeta} is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by definition of $\bbeta_t(\delta)$ and Lemma \ref{lem:detVt}. The third inequality \eqref{eq:pfMCmeaneq} is because of mean inequality. The forth inequality \eqref{eq:pfMCsumXi} is by the definition of $\beta_t(\delta)$ and Lemma \ref{lem:SumXiEstimateInDet}. And the last inequality \eqref{eq:pfMCdetEst} is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
\end{proof}
